Global Illumination for Fun and Profit

### 2022-02-22 paper.qmd
more

---
# Quarto-specific stuff you probably don't want to change for now
pdf-engine: pdflatex
documentclass: vgtc
cite-method: natbib
natbiboptions: square, numbers
format:
  pdf:
    template: tvcg.latex
  latex:
    template: tvcg.latex
#  Uncomment the two lines below to also generate an HTML version
#  html:
#    dummy: unused

>>>>

---
# Quarto-specific stuff you probably don't want to change for now
pdf-engine: pdflatex
documentclass: vgtc
cite-method: natbib
natbiboptions: square, numbers
format:
  pdf:
    template: vgtc-quarto-template/tvcg.latex
  latex:
    template: vgtc-quarto-template/tvcg.latex
#  Uncomment the two lines below to also generate an HTML version
#  html:
#    dummy: unused
